Check model

### 2024-03-27 Code/00_PrepareTrainingData_save.Rmd
Final edits
Added instability plot

### Load packages, functions, and data 
```{r, eval=TRUE, echo=TRUE, message=FALSE, warning=FALSE}
# erase memory
rm(list = ls(all.names = TRUE))

@@

# Prepare Multiple imputation
```{r, eval=TRUE}
variables.to.be.imputed <- c("Center", "SNstatus", "Sex", "Age.SN", "Ulceration",
                             "Loc_CAT", "Histology", "Breslow", "multiple.fields",
                             "Tot_SNs_neg", "Tot_SNs_pos", "Rdamcrit", "Dewar",
                             "Mitosis", "Status", 
                             "Rec.composite", "logRec.composite.time",
                             "MSM", "logFU.time")
training.data.to.be.imputed <- sel.train.data[, variables.to.be.imputed]
missings.table(training.data.to.be.imputed)
```

>>>>

### Load packages, functions, and data 
```{r, eval=TRUE, echo=TRUE, message=FALSE, warning=FALSE}
# erase memory
# rm(list = ls(all.names = TRUE))

@@

# Prepare Multiple imputation
```{r, eval=TRUE}
variables.to.be.imputed <- c("Center", "SNstatus", "Sex", "Age.SN", "Ulceration",
                             "Loc_CAT", "Histology", "Breslow", "multiple.fields",
                             "Tot_SNs_neg", "Tot_SNs_pos", "Rdamcrit", "Dewar",
                             "Mitosis", "Status", 
                             "Rec.composite", "logRec.composite.time",
                             "MSM", "logFU.time")
                             # "SNdate", "Date_1st_Rec", "Last_FU")
training.data.to.be.imputed <- sel.train.data[, variables.to.be.imputed]
missings.table(training.data.to.be.imputed)
```

### 2024-03-27 Code/11_TestModel.Rmd
Added instability plot

# load libraries
library(rms)
library(survival)
source("Z:/Project Melanoom/PaperMelanoma/Code/PaperMelanomaFunctions.R")
```

@@

### Test proportional hazards assumption
```{r, eval=TRUE}
test.prop<-survival::cox.zph(f.mi.full.Rec.5$fits[[1]])
test.prop
plot(test.prop)
```
### See if RFS always lower than MSS
```{r, eval=TRUE}
p.RFS <- fun.event(lp=predict(f.mi.BS.Rec.5), h0=h0.Rec)
p.MSS <- fun.event(lp=MSM.cal.fact*predict(f.mi.BS.Rec.5), h0=h0.MSM)
plot(p.RFS, p.MSS)
abline(a=0, b=1, col="red")
```

>>>>

# load libraries
library(dplyr)
library(rms)
library(survival)
source("Z:/Project Melanoom/PaperMelanoma/Code/PaperMelanomaFunctions.R")
```

@@

### Test proportional hazards assumption
```{r, eval=TRUE}
test.prop<-survival::cox.zph(f.mi.full.Rec.5$fits[[1]])
test.prop
plot(test.prop)
```
### See if RFS always lower than MSS
```{r, eval=TRUE}
p.RFS <- fun.event(lp=predict(f.mi.BS.Rec.5), h0=h0.Rec)
p.MSS <- fun.event(lp=MSM.cal.fact*predict(f.mi.BS.Rec.5), h0=h0.MSM)
plot(p.RFS, p.MSS)
abline(a=0, b=1, col="red")
```
# Stability plot
```{r, eval=TRUE}
# give each individual a unique ID
last.imputed.training.data.set$ID <- 1:nrow(last.imputed.training.data.set)

# fit model
final.model <- cph(form.BS.Rec.5, data=last.imputed.training.data.set, y=TRUE, x=TRUE, se.fit=TRUE)

# get linear predictor
lp.final <- predict(final.model, type="lp")

# obtain baseline hazard
f.basehaz.final <- survival::basehaz(final.model)
h0.final <- f.basehaz.final$hazard[f.basehaz.final$time==max(f.basehaz.final$time[f.basehaz.final$time<=horizon])]

# obtain probability prediction
p.original <- fun.event(h0=h0.final, lp=lp.final)

# check final model
SF<-survival::survfit(S.Rec.5.training~1,data=last.imputed.training.data.set)
cat(" KM      :", (1-SF$surv[SF$time==max(SF$time[SF$time<=horizon])]), "\n",
    "avg pred:", mean(p.original), "\n")

# fit model on bootstrapped sample
p.boot <- c()
B <- 200
set.seed(1)
for (i in 1:B){
  # bootstrap sample
  boot.indices <- sample(last.imputed.training.data.set$ID, 
                             nrow(last.imputed.training.data.set), 
                             replace=TRUE)
  bootstrap.sample <- last.imputed.training.data.set[boot.indices,]
  S.boot <- S.Rec.5.training[boot.indices,]

  # fit model on bootstrap
  form.boot <- update(form.BS.Rec.5, S.boot ~ .)
  boot.model <- cph(form.boot, data=bootstrap.sample, y=TRUE, x=TRUE, se.fit=TRUE)

  # linear predictor
  lp.b <- predict(boot.model, newdata=last.imputed.training.data.set, type="lp")

  # baseline hazard
  f.basehaz.boot <- survival::basehaz(boot.model)
  h0.boot <- f.basehaz.boot$hazard[f.basehaz.boot$time==max(f.basehaz.boot$time[f.basehaz.boot$time<=horizon])]

  # predict probability
  p.boot <- c(p.boot, fun.event(h0=h0.boot, lp=lp.b))

  # check bootstrapped model
  SF.boot<-survival::survfit(S.Rec.5.training~1, data=bootstrap.sample)
  # cat(" KM      :", (1-SF.boot$surv[SF.boot$time==max(SF.boot$time[SF.boot$time<=horizon])]), "\n",
  #     "avg pred:", mean(p.boot), "\n")
}
p.df <- data.frame(p.original=rep(p.original, B), p.boot=p.boot)
```
```{r, eval=TRUE}
library(ggplot2)
ggplot(data=p.df, 
       mapping=aes(x=p.original, y=p.boot))+
  geom_point(alpha=0.3)+
  geom_abline(intercept=0, slope=1)+
  ylim(c(0, 1))+ylab("Predictions using bootstrap models")+
  xlim(c(0, 1))+xlab("Prediction using original model")+
  theme_bw()
```
```{r,eval=TRUE}
library(dcurves)
dca(S ~ Model, data=data.frame(S=S.Rec.training, Model=p.RFS), time=5) %>% plot(smooth=TRUE)
dca(S ~ Model, data=data.frame(S=S.MSM.training, Model=p.MSS), time=5) %>% plot(smooth=TRUE)
```
